%-------------------------
% Tailored Resume for NVIDIA Software Engineering Internships (2026)
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lin Hong} \\ \vspace{1pt}
    \small \href{mailto:linlin.hong1@gmail.com}{\underline{linlin.hong1@gmail.com}} $|$
    \href{https://github.com/LinHong149}{\underline{github.com/LinHong149}} $|$
    \href{https://linkedin.com/in/linhongdev}{\underline{linkedin.com/in/linhongdev}} $|$
    \href{https://linhong.dev}{\underline{linhong.dev}} \\
    \vspace{3pt}
    \small 10× Hackathon Winner · 2× Founding Engineer · Systems \& Full-Stack Developer
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Sept 2024 -- Apr 2028}
      {Bachelor of Computer Science (Co-op)}{}
      \resumeItemListStart
        \resumeItem{President’s Scholarship of Distinction, Ted Rogers Future Leaders Scholarship for Women}
        \resumeItem{Relevant coursework: Intro to CS, Algorithm Design, Data Abstraction, Calculus 1 \& 2}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Go, Java, C++, JavaScript, TypeScript, Bash, PHP, HTML/CSS, Tailwind \\
     \textbf{Technologies:} Git, Next.js, React, Flask, FastAPI, Docker, AWS, PostgreSQL, Redis, Nginx, Cloudflare R2 \\
     \textbf{Systems:} Linux, TCP/IP \& DNS fundamentals, reverse proxying, RESTful API design, microservices orchestration
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote AI}{July 2025 -- Present}
      {Founding Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Cut rendering latency 5× by chunking video jobs across Celery workers with \textbf{Redis} queues, parallelized stages, and resilient retries.}
        \resumeItem{Containerized \textbf{FastAPI} services and async Celery workers with \textbf{Docker}, shipped via GitHub Actions for predictable releases.}
        \resumeItem{Delivered real-time collaboration through Clerk auth, WebSockets, \textbf{Redis} pub/sub, and Neon-hosted \textbf{PostgreSQL} to keep multi-user edits consistent.}
      \resumeItemListEnd

    \resumeSubheading
      {FTC Robotics}{Sept 2022 -- June 2025}
      {Senior Software Lead}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Engineered telemetry pipelines aggregating encoder, IMU, and camera data into unified robot state estimation in \textbf{C++} for reliable control loops.}
        \resumeItem{Designed filtering and validation logic to suppress noisy sensor data, boosting reliability by 20\% and doubling control response speed during competition runs.}
        \resumeItem{Implemented PID tuning with hardware engineers, improving autonomous navigation accuracy by 70\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Linovation Design}{Summer 2024}
      {Full Stack Developer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Designed and launched 8 production websites using Next.js/\textbf{TypeScript}, React, Tailwind, and Figma for responsive user experiences.}
        \resumeItem{Built \textbf{Flask} APIs with JWT auth, database integrations, and \textbf{Docker} deployment across Vercel and MongoDB to harden releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{HomeLab} $|$ \emph{Linux, Docker, Nginx, Cloudflare}}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Provisioned a \textbf{Linux} server with SSH keys, TLS termination, and \textbf{Nginx} reverse proxying routed through \textbf{Cloudflare} DNS/proxy for secure access.}
        \resumeItem{Run containerized services with \textbf{Docker} and PM2, adding health checks and centralized logs for quick rollback.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Spotilike} $|$ \emph{Flask, Next.js, TensorFlow, DeepFace}}{June 2025}
      \resumeItemListStart
        \resumeItem{Built an AI-driven music discovery app linking emotion embeddings to tracks with \textbf{TensorFlow} and \textbf{DeepFace} inference.}
        \resumeItem{Served recommendations through \textbf{Flask} APIs and a \textbf{Next.js} frontend integrating Spotify for real-time playback, tuned with batched inference to keep responses snappy.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Skip the Walk} $|$ \emph{Terraform, Commander.js, Slack API}}{Sept 2024}
      \resumeItemListStart
        \resumeItem{Built a CLI automating Domino’s ordering and volunteer routing with \textbf{Terraform}-defined workflows and Slack notifications.}
        \resumeItem{Integrated Mappedin indoor navigation plus retries and per-step logging to keep runs resilient across flaky venue Wi-Fi at \textbf{Hack the North}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
