%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Adapted for Lin Hong
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lin Hong} \\ \vspace{1pt}
    \small \href{mailto:linlin.hong1@gmail.com}{\underline{linlin.hong1@gmail.com}} $|$
    \href{https://github.com/LinHong149}{\underline{github.com/LinHong149}} $|$
    \href{https://linkedin.com/in/linhongdev}{\underline{linkedin.com/in/linhongdev}} $|$
    \href{https://linhong.dev}{\underline{linhong.dev}} \\
    \vspace{3pt}
    \small 10× Hackathon Winner · 2× Founding Engineer · Full-Stack \& AI Developer
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Waterloo}{Sept 2024 -- Apr 2028}
      {Bachelor of Computer Science (Co-op)}{}
      \resumeItemListStart
        \resumeItem{President’s Scholarship of Distinction, Ted Rogers Future Leaders Scholarship for Women}
        \resumeItem{Relevant coursework: Intro to CS, Algorithm Design, Data Abstraction, Calculus 1 \& 2}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Go, Java, C++, JavaScript, TypeScript, Bash, PHP, HTML/CSS, Tailwind \\
     \textbf{Technologies:} Git, Next.js, React, Flask, FastAPI, Docker, AWS, PostgreSQL, MongoDB, Nginx, Pytorch
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote AI}{July 2025 -- Present}
      {Founding Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Optimized a large-scale video rendering pipeline, reducing processing time by 5× through segment-based parallelization and backend optimizations.}
        \resumeItem{Implemented Clerk authentication with WebSockets, enabling real-time sync and Redis pub/sub event broadcasting into a Neon-hosted PostgreSQL database.}
        \resumeItem{Built scalable REST APIs using FastAPI, Dockerized services, and asynchronous Celery workers orchestrated through Redis.}
        \resumeItem{Deployed frontend to Vercel and backend to Render, utilizing Cloudflare R2 for object storage and GitHub Actions for CI/CD.}
      \resumeItemListEnd

    \resumeSubheading
      {FTC Robotics}{Sept 2022 -- June 2025}
      {Senior Software Lead}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Engineered telemetry pipelines aggregating encoder, IMU, and camera data into unified robot state estimation.}
        \resumeItem{Designed signal filtering and validation logic to eliminate noisy sensor readings, improving reliability by 20\% and doubling response speed.}
        \resumeItem{Implemented PID tuning with hardware engineers, improving autonomous navigation accuracy by 70\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Linovation Design}{Summer 2024}
      {Full Stack Developer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Designed and launched 8 production websites using Next.js, React, TypeScript, Tailwind, and Figma.}
        \resumeItem{Built Flask APIs with JWT authentication and database integrations; deployed using Docker, Vercel, and MongoDB.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{HomeLab} $|$ \emph{Linux, Docker, Nginx, Cloudflare}}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built a personal Linux server secured with SSH key-pair authentication and HTTPS reverse proxying.}
        \resumeItem{Deployed Dockerized Node.js apps with PM2 and Cloudflare DNS/routing for secure access.}
        \resumeItem{Developed an understanding of TCP/IP fundamentals, load balancing, and CDN architectures.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Chess Bot} $|$ \emph{PyTorch, Modal, Python}}{June 2025}
      \resumeItemListStart
        \resumeItem{Built an AlphaZero-style chess engine with a unified policy–value network trained via large-scale self-play reinforcement learning.}
        \resumeItem{Integrated neural priors into Monte Carlo Tree Search to guide node expansion, improving playing strength and convergence stability.}
        \resumeItem{Ran distributed training and self-play generation on A100/H100 GPUs via Modal, achieving high-throughput RL cycles and automated checkpoint evaluation.}
        \resumeItem{Reached $\sim$1600 Elo strength against classical engines through iterative self-play and MCTS-guided training.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Spotilike} $|$ \emph{Flask, Next.js, Tailwind, TensorFlow, DeepFace}}{June 2025}
      \resumeItemListStart
        \resumeItem{Created an AI-driven music discovery platform that matches songs to user emotions in real time.}
        \resumeItem{Integrated DeepFace, OpenCV, TensorFlow, Gemini, and Spotify API for emotion-aware track recommendations.}
        \resumeItem{Designed MongoDB schemas linking emotion embeddings to music metadata.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Lofied} $|$ \emph{Python, torchaudio, Pedalboard}}{May 2025}
      \resumeItemListStart
        \resumeItem{Developed a Python tool converting Spotify playlists to lo-fi tracks using DSP and Spotify API.}
        \resumeItem{Implemented Basic Pitch for audio-to-sheet-music conversion and Docker-based deployment.}
        \resumeItem{Won Best Solo Hack \& Top 6 Overall at JamHacks 2025.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Skip the Walk} $|$ \emph{Terraform, Commander.js, Slack API}}{Sept 2024}
      \resumeItemListStart
        \resumeItem{Built a CLI to automate Domino’s pizza ordering and volunteer routing at Hack the North.}
        \resumeItem{Integrated Mappedin for indoor navigation and Terraform for workflow automation.}
        \resumeItem{Won Best Use of Terraform at Hack the North 2024.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Flaim Brain} $|$ \emph{Flask, LangChain, MongoDB}}{Jan 2024}
      \resumeItemListStart
        \resumeItem{Implemented an AI mentor enabling file uploads, note summarization, and personalized study guides.}
        \resumeItem{Used GPT-4, Cloud Vision, and MongoDB Atlas Vector Search to provide semantic retrieval.}
        \resumeItem{Placed 4th at Hack the Valley 8 among 80 teams.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Bill-in-Bytes} $|$ \emph{React Native, Google Cloud Vision}}{May 2023}
      \resumeItemListStart
        \resumeItem{Digitized paper receipts into structured data using OCR for easier expense tracking.}
        \resumeItem{Won Best UI/UX Hack \& People's Choice at GryphHacks 2023.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Ingredify} $|$ \emph{React Native, Cohere, MongoDB}}{July 2023}
      \resumeItemListStart
        \resumeItem{Extracted ingredient text using Tesseract OCR and analyzed health effects with Cohere NLP.}
        \resumeItem{Built personalized dietary recommendation features using MongoDB and React Native.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Inner Voice} $|$ \emph{Next.js, Whisper, OpenAI TTS}}{July 2023}
      \resumeItemListStart
        \resumeItem{Built a multi-persona speech AI app with full STT and TTS accessibility.}
        \resumeItem{Integrated OpenAI APIs for persona generation and conversation flows.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}