%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Adapted for Ri Hong
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ri Hong} \\ \vspace{1pt}
    \small \href{mailto:riri.hong@gmail.com}{\underline{riri.hong@gmail.com}} $|$
    \href{https://github.com/Ri-Hong}{\underline{github.com/Ri-Hong}} $|$
    \href{https://linkedin.com/in/ririhong}{\underline{linkedin.com/in/ririhong}} \\
    Production Engineering \& Infrastructure 路 Backend Systems 路 Kubernetes \& Cloud 路 Linux Systems
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Bachelor of Computer Science (Co-op) 路 GPA: 3.9/4.0}{2022 -- 2027}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Algorithms, Data Structures, Databases, Object-Oriented Programming, Systems Programming}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Go, Python, C/C++, Java, TypeScript, JavaScript \\
     \textbf{Infrastructure:} Linux, Kubernetes, Docker, Terraform, AWS, GCP, Ansible, CI/CD \\
     \textbf{Systems:} gRPC, PostgreSQL, Temporal, OpenTelemetry, Networking, Load Balancing
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Groq}{Sept 2025 -- Dec 2025}
      {Cloud Engineering Intern}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Engineered multi-region production infrastructure with Terraform, Kubernetes, Kustomize, and Flux on GCP, enabling horizontally scalable workloads and reducing deployment time by 24\% through infrastructure automation.}
        \resumeItem{Debugged and optimized production systems handling large-scale AI/ML workloads, ensuring reliability and performance across distributed infrastructure.}
      \resumeItemListEnd

    \resumeSubheading
      {Base Power}{Jan 2025 -- Apr 2025}
      {Software Engineering Intern}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable backend infrastructure and production systems in a high-ownership environment, optimizing critical trading workflows for a Series B energy startup.}
        \resumeItem{Reduced simulation time by 5x by redesigning the simulation engine for Kubernetes-based parallel processing, implementing distributed systems patterns and monitoring with OpenTelemetry.}
        \resumeItem{Migrated local simulations to Temporal Cloud with intermediate state persistence in AWS S3, implementing fault-tolerant retry mechanisms for production reliability.}
        \resumeItem{Implemented concurrent batch publishing with Goroutines, increasing BigQuery throughput by 32\%, and reduced redundant runs by 47\% via input hashing to optimize resource utilization.}
      \resumeItemListEnd

    \resumeSubheading
      {Walnote.ai}{Aug 2025 -- Present}
      {Founder \& CTO}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Built and scaled production backend infrastructure with Docker, FastAPI, and Celery, processing 1,000+ animations with distributed GPU rendering pipelines.}
        \resumeItem{Optimized system performance by segmenting code generation and implementing distributed rendering, reducing render latency from 12s to 2s via pipelined streaming workflows.}
        \resumeItem{Designed secure, scalable infrastructure with Docker, Cloudflare R2, and PostgreSQL, leading product strategy from prototype to production deployment.}
      \resumeItemListEnd

    \resumeSubheading
      {GeeseHacks}{May 2024 -- Feb 2025}
      {Lead Software Engineer}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Led an 8-person engineering team to build core infrastructure for a 600+ attendee hackathon, ensuring system reliability under high load.}
        \resumeItem{Developed a real-time backend system with PostgreSQL and REST APIs, handling 5,000+ concurrent score updates with sub-200ms latency.}
        \resumeItem{Built CI/CD workflows with GitHub Actions for automated deployment to staging and production environments.}
      \resumeItemListEnd

    \resumeSubheading
      {Trend Micro}{May 2024 -- Aug 2024}
      {Software Engineering Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Modernized a 1.2M-line production Java codebase by upgrading Deep Security Manager from JDK 8 to 11, unlocking 40+ dependency updates and reducing CI build time by 18\% through infrastructure optimization.}
      \resumeItemListEnd

    \resumeSubheading
      {Microgreen Solar}{Sept 2023 -- Dec 2023}
      {Software Engineering Intern}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Built a production telemetry ingestion pipeline with AWS IoT Core and AWS RDS for real-time off-grid energy monitoring, handling high-throughput data streams.}
        \resumeItem{Optimized backend performance by introducing Redis caching, reducing query latency from 5000ms to 100ms for production workloads.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{HomeLab} $|$ \emph{Linux, Proxmox, Ansible, Kubernetes}}{Apr 2025}
      \resumeItemListStart
        \resumeItem{Deployed and managed a production-grade Kubernetes cluster on Proxmox using Terraform and Ansible, implementing scalable, self-healing microservices with Nginx load balancing and Cloudflare HTTPS routing for high-availability infrastructure.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

