%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Adapted for Lin Hong
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lin Hong} \\ \vspace{1pt}
    \small \href{mailto:linlin.hong1@gmail.com}{\underline{linlin.hong1@gmail.com}} $|$
    \href{https://github.com/LinHong149}{\underline{github.com/LinHong149}} $|$
    \href{https://linkedin.com/in/linhongdev}{\underline{linkedin.com/in/linhongdev}} $|$
    \href{https://linhong.dev}{\underline{linhong.dev}} \\
    \vspace{3pt}
    \small 10× Hackathon Winner · Deep Learning Engineer · GPU Computing
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Waterloo}{Sept 2024 -- Apr 2028}
      {Bachelor of Computer Science (Co-op)}{}
      \resumeItemListStart
        \resumeItem{President's Scholarship of Distinction, Ted Rogers Future Leaders Scholarship for Women}
        \resumeItem{Relevant coursework: Deep Neural Networks, Linear Algebra, Numerical Methods, Computer Vision, Computer Architecture, Algorithm Design, Data Abstraction}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, C++, Go, Java, JavaScript, TypeScript, Bash \\
     \textbf{Technologies:} PyTorch, TensorFlow, CUDA, GPU Programming, Docker, AWS, Linux, Git, FastAPI, PostgreSQL
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote AI}{July 2025 -- Present}
      {Founding Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Optimized large-scale video rendering pipeline, reducing processing time by 5× through segment-based parallelization and performance-oriented backend optimizations.}
        \resumeItem{Implemented Clerk authentication with WebSockets, enabling real-time sync and Redis pub/sub event broadcasting into a Neon-hosted PostgreSQL database.}
        \resumeItem{Built scalable REST APIs using FastAPI, Dockerized services, and asynchronous Celery workers orchestrated through Redis for high-throughput data processing.}
        \resumeItem{Deployed frontend to Vercel and backend to Render, utilizing Cloudflare R2 for object storage and GitHub Actions for CI/CD.}
      \resumeItemListEnd

    \resumeSubheading
      {FTC Robotics}{Sept 2022 -- June 2025}
      {Senior Software Lead}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Engineered telemetry pipelines aggregating encoder, IMU, and camera data into unified robot state estimation using numerical methods and signal filtering.}
        \resumeItem{Designed signal filtering and validation logic to eliminate noisy sensor readings, improving reliability by 20\% and doubling response speed.}
        \resumeItem{Implemented PID tuning with hardware engineers, improving autonomous navigation accuracy by 70\% through algorithmic optimization.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Chess Bot} $|$ \emph{\textbf{PyTorch}, \textbf{GPU}, Modal, Python}}{June 2025}
      \resumeItemListStart
        \resumeItem{Built an AlphaZero-style chess engine with unified policy–value \textbf{deep neural network} trained via large-scale self-play reinforcement learning on \textbf{A100/H100 GPUs}.}
        \resumeItem{Integrated neural priors into Monte Carlo Tree Search to guide node expansion, improving playing strength and convergence stability.}
        \resumeItem{Ran distributed training and self-play generation on \textbf{A100/H100 GPUs} via Modal, achieving high-throughput RL cycles and automated checkpoint evaluation.}
        \resumeItem{Reached $\sim$1600 Elo strength against classical engines through iterative self-play and MCTS-guided training with performance-optimized \textbf{GPU} implementations.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Spotilike} $|$ \emph{\textbf{TensorFlow}, \textbf{DeepFace}, Computer Vision, OpenCV}}{June 2025}
      \resumeItemListStart
        \resumeItem{Created AI-driven music platform using \textbf{TensorFlow} and \textbf{DeepFace} for real-time emotion recognition from facial expressions via \textbf{computer vision} pipelines.}
        \resumeItem{Integrated OpenCV, Gemini API, and Spotify API to provide emotion-aware track recommendations with optimized inference performance.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Lofied} $|$ \emph{Python, \textbf{torchaudio}, Pedalboard, DSP}}{May 2025}
      \resumeItemListStart
        \resumeItem{Developed a Python tool converting Spotify playlists to lo-fi tracks using \textbf{torchaudio} for audio processing, DSP algorithms, and Spotify API integration.}
        \resumeItem{Implemented Basic Pitch for audio-to-sheet-music conversion and Docker-based deployment; won Best Solo Hack \& Top 6 Overall at JamHacks 2025.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

