%-------------------------
% Tailored Resume for Microsoft Software Engineering Explore Intern
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lin Hong} \\ \vspace{1pt}
    \small \href{mailto:linlin.hong1@gmail.com}{\underline{linlin.hong1@gmail.com}} $|$
    \href{https://github.com/LinHong149}{\underline{github.com/LinHong149}} $|$
    \href{https://linkedin.com/in/linhongdev}{\underline{linkedin.com/in/linhongdev}} $|$
    \href{https://linhong.dev}{\underline{linhong.dev}} \\
    \vspace{3pt}
    \small 10× Hackathon Winner · Software Engineering Explore Intern · Product-Focused Developer
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Waterloo}{Sept 2025 -- Apr 2029}
      {Bachelor of Computer Science (Co-op)}{}
      \resumeItemListStart
        \resumeItem{President's Scholarship of Distinction, Ted Rogers Future Leaders Scholarship for Women}
        \resumeItem{Relevant coursework: Intro to CS, Data Structures, Algorithm Design, Software Engineering Principles}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Java, C++, JavaScript, TypeScript, Go, Bash, HTML/CSS \\
     \textbf{Technologies:} Git, React, Next.js, Flask, FastAPI, Docker, PostgreSQL, MongoDB, AWS, Azure, GitHub Actions
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote AI}{July 2025 -- Present}
      {Founding Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Shipped \textbf{10+} full-stack features using \textbf{Python}, \textbf{FastAPI}, and React, reducing user onboarding flow time by \textbf{30\%} and increasing weekly active sessions by \textbf{$\sim$25\%}.}
        \resumeItem{Designed and optimized \textbf{backend APIs} and data pipelines on \textbf{PostgreSQL} and \textbf{Redis}, cutting p95 request latency by \textbf{40\%} and eliminating multiple production timeouts.}
        \resumeItem{Improved release reliability by \textbf{introducing CI/CD} with \textbf{GitHub Actions} and code review checklists, driving a noticeable drop in post-release bug reports from teammates.}
      \resumeItemListEnd

    \resumeSubheading
      {Linovation Design}{Summer 2024}
      {Full Stack Developer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Delivered \textbf{8} production marketing sites for local clients using \textbf{React}, \textbf{Next.js}, and \textbf{TypeScript}, helping several businesses move from no web presence to live, production-ready experiences.}
        \resumeItem{Built \textbf{Flask} APIs with authentication and database integrations, reducing manual content-update work for clients by \textbf{$\sim$50\%} through simple dashboards and forms.}
        \resumeItem{Containerized services with \textbf{Docker} and deployed to Vercel/\textbf{MongoDB} Atlas, standardizing the deployment pipeline and cutting setup time for new projects from days to hours.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Chess Bot} $|$ \emph{PyTorch, Modal, \textbf{Python}}}{June 2025}
      \resumeItemListStart
        \resumeItem{Built an AlphaZero-style \textbf{reinforcement learning} chess engine with a unified policy–value network in \textbf{PyTorch}, running large-scale self-play on cloud GPUs via Modal.}
        \resumeItem{Reached $\sim$\textbf{1600 Elo} strength against classical engines through iterative training and automated evaluation, after integrating Monte Carlo Tree Search with neural priors.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Spotilike} $|$ \emph{Flask, Next.js, TensorFlow}}{June 2025}
      \resumeItemListStart
        \resumeItem{Created an \textbf{AI-powered} music discovery web app that maps real-time emotion signals to tracks, integrating \textbf{Flask} backend, \textbf{Next.js} frontend, and \textbf{Spotify API}.}
        \resumeItem{Collaborated with teammates to iterate on UI flows and recommendation logic, improving engagement metrics such as song skip rate in user testing.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Skip the Walk} $|$ \emph{Terraform, Commander.js, Slack API}}{Sept 2024}
      \resumeItemListStart
        \resumeItem{Built a CLI tool in \textbf{Node.js}/Commander.js to automate Domino's pizza ordering and volunteer routing for Hack the North, saving organizers hours of manual coordination.}
        \resumeItem{Integrated \textbf{Terraform} and Slack API to provision workflows and send real-time updates, winning \textbf{Best Use of Terraform} out of dozens of submitted projects.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Inner Voice} $|$ \emph{Next.js, Whisper, OpenAI TTS}}{July 2023}
      \resumeItemListStart
        \resumeItem{Built a multi-persona speech \textbf{AI} app with full STT and TTS accessibility using \textbf{Next.js}, OpenAI \textbf{Whisper}, and TTS APIs, enabling hands-free interaction.}
        \resumeItem{Implemented persona-based conversation flows that adapt to user tone and history, showcasing experience integrating external \textbf{AI APIs} into a polished front-end experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
