%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Adapted for Ri Hong
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ri Hong} \\ \vspace{1pt}
    \small \href{mailto:riri.hong@gmail.com}{\underline{riri.hong@gmail.com}} $|$
    \href{https://github.com/Ri-Hong}{\underline{github.com/Ri-Hong}} $|$
    \href{https://linkedin.com/in/ririhong}{\underline{linkedin.com/in/ririhong}} \\ \vspace{3pt}
    \small 10× Hackathon Winner · Fullstack Engineer · Product Engineer
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{2022 -- 2027}
      {Bachelor of Computer Science (Co-op) · GPA: 3.9/4.0}{}
      \resumeItemListStart
        \resumeItem{Relevant coursework: Algorithms, Data Structures, Object-Oriented Programming, Databases, Operating Systems, Computer Networks}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} JavaScript, TypeScript, Python, Java, C/C++, Go, HTML, CSS \\
     \textbf{Technologies:} React, Next.js, Docker, PostgreSQL, AWS, Linux, Kubernetes, Terraform \\
     \textbf{Tools:} Git, Jest, Cypress, GitHub Actions, CI/CD
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote.ai}{Aug 2025 -- Present}
      {Founder \& CTO}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Launched an AI platform combining GPT-5 with Manim to auto-generate explainer videos; processed 1,000+ animations with a \textbf{Python} + \textbf{FastAPI} pipeline.}
        \resumeItem{Accelerated generation by segmenting code generation and running distributed GPU rendering, reducing render latency from 12s to 2s; leveraging a pipelined streaming workflow to deliver near real-time playback.}
        \resumeItem{Scaled secure rendering and delivery with \textbf{Docker}, FFmpeg, Cloudflare R2, and \textbf{PostgreSQL}; raised \$20k pre-seed and led product strategy from prototype to production.}
      \resumeItemListEnd

    \resumeSubheading
      {Base Power}{Jan 2025 -- Apr 2025}
      {Software Engineering Intern}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Led fullstack and infrastructure initiatives in a mission-critical environment, collaborating with algorithm developers to improve energy trading performance in a Series B (\$850M) startup.}
        \resumeItem{Discovered and resolved a performance bug in real-time market data transformation logic, reducing complexity from O(n²) to O(n log n) by applying \textbf{algorithm} optimization techniques.}
        \resumeItem{Rewrote market controller UI using \textbf{React} and \textbf{Next.js}, allowing on-call traders to execute trades within seconds.}
      \resumeItemListEnd

    \resumeSubheading
      {Groq}{Sept 2025 -- Dec 2025}
      {Software Engineering Intern}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Designed and launched an observability platform to measure engineering productivity and AI coding tool adoption (Claude Code, Cursor, AmpCode), providing actionable insights for 400+ engineers.}
        \resumeItem{Developed dashboards and analytics workflows that surfaced correlations between AI tool usage and code quality, driving data-informed adoption strategies.}
      \resumeItemListEnd

    \resumeSubheading
      {GeeseHacks}{May 2024 -- Feb 2025}
      {Lead Software Developer}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Led a team of 8 developers to develop the software infrastructure for a first-time hackathon with 600+ attendees, achieving 98\% uptime during the event and securing \$25k in funding.}
        \resumeItem{Cultivated a quality-first culture by incorporating \textbf{Jest} and \textbf{Cypress} for testing, achieving 98\% test coverage; optimized application performance using \textbf{Next.js}, achieving 25\% faster page load time.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Trasee} $|$ \emph{Pyodide, React, TypeScript, Vite, React Flow}}{Oct 2025}
      \resumeItemListStart
        \resumeItem{Built a real-time \textbf{Python} code visualizer that intelligently recognizes \textbf{data structures} and renders them interactively in the browser; engineered a two-phase static + runtime analysis pipeline using \textbf{Python}'s ast module and \textbf{Pyodide} WebAssembly.}
        \resumeItem{Designed a performant time-travel debugger with memoized \textbf{React} renders and Monaco Editor integration; won ``Best Revolutionizing Learning Hack'' at Hack the Valley X among 100+ teams.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Neural Style Transfer Engine} $|$ \emph{PyTorch, CUDA, FastAPI, Docker}}{Sept 2025}
      \resumeItemListStart
        \resumeItem{Engineered a high-performance Neural Style Transfer system with custom CUDA kernels for Gram matrix computation, achieving 8x faster style transfer compared to CPU-only implementation.}
        \resumeItem{Built a scalable REST API with \textbf{FastAPI} for style transfer requests, containerized with \textbf{Docker} for easy deployment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

