%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Adapted for Lin Hong
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lin Hong} \\ \vspace{1pt}
    \small \href{mailto:linlin.hong1@gmail.com}{\underline{linlin.hong1@gmail.com}} $|$
    \href{https://github.com/LinHong149}{\underline{github.com/LinHong149}} $|$
    \href{https://linkedin.com/in/linhongdev}{\underline{linkedin.com/in/linhongdev}} $|$
    \href{https://linhong.dev}{\underline{linhong.dev}} \\
    \vspace{3pt}
    \small 10× Hackathon Winner · AI/ML Engineer · Software Engineer
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Waterloo}{Sept 2024 -- Apr 2028}
      {Bachelor of Computer Science (Co-op)}{}
      \resumeItemListStart
        \resumeItem{President's Scholarship of Distinction, Ted Rogers Future Leaders Scholarship for Women}
        \resumeItem{Relevant coursework: Algorithm Design, Data Structures, Machine Learning, Data Abstraction, Statistics}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Java, C++, JavaScript, TypeScript, Go, Bash, HTML/CSS \\
     \textbf{Technologies:} \textbf{PyTorch}, \textbf{TensorFlow}, \textbf{scikit-learn}, FastAPI, Flask, Docker, PostgreSQL, MongoDB, Git, AWS
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote AI}{July 2025 -- Present}
      {Founding Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Built scalable software solutions using \textbf{Python} and FastAPI, implementing \textbf{AI}-powered video processing pipelines that reduced processing time by 5× through distributed computing.}
        \resumeItem{Collaborated with cross-functional teams to design and implement real-time data pipelines, integrating \textbf{machine learning} models for intelligent content processing and analytics.}
        \resumeItem{Applied software engineering best practices including code reviews, testing, and CI/CD automation to ensure product quality and reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {FTC Robotics}{Sept 2022 -- June 2025}
      {Senior Software Lead}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Engineered telemetry pipelines processing encoder, IMU, and camera data using \textbf{object-oriented} design principles in \textbf{C++} and \textbf{Java} for real-time robot state estimation.}
        \resumeItem{Designed and implemented signal processing algorithms with validation logic, improving system reliability by 20\% through iterative testing and refinement.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Chess Bot} $|$ \emph{\textbf{PyTorch}, Modal, \textbf{Python}}}{June 2025}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{machine learning} model using \textbf{PyTorch} with a unified policy–value network trained via large-scale self-play reinforcement learning on A100/H100 GPUs.}
        \resumeItem{Implemented Monte Carlo Tree Search with neural priors, achieving $\sim$1600 Elo strength through iterative model refinement and automated evaluation pipelines.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Spotilike} $|$ \emph{Flask, \textbf{TensorFlow}, DeepFace}}{June 2025}
      \resumeItemListStart
        \resumeItem{Created an \textbf{AI}-driven music discovery platform using \textbf{TensorFlow} and DeepFace for real-time emotion recognition, implementing \textbf{ML} models for personalized track recommendations.}
        \resumeItem{Built full-stack application with \textbf{Python} backend and Next.js frontend, processing large datasets and integrating Spotify API for emotion-aware music matching.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Flaim Brain} $|$ \emph{Flask, LangChain, MongoDB}}{Jan 2024}
      \resumeItemListStart
        \resumeItem{Implemented an \textbf{AI} mentor platform using GPT-4 and Cloud Vision APIs, processing file uploads and generating personalized study guides through \textbf{machine learning}-powered semantic retrieval.}
        \resumeItem{Designed and deployed \textbf{AI} solution with MongoDB Atlas Vector Search, enabling intelligent content analysis and recommendation systems.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Inner Voice} $|$ \emph{Next.js, Whisper, OpenAI TTS}}{July 2023}
      \resumeItemListStart
        \resumeItem{Built a multi-persona speech \textbf{AI} application using OpenAI Whisper for speech-to-text and TTS APIs, implementing \textbf{machine learning} models for natural language understanding and conversation generation.}
        \resumeItem{Developed full-stack application with Next.js, integrating \textbf{AI} APIs for persona generation and real-time conversation flows with intelligent response processing.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

