%-------------------------
% Tailored Resume for Microsoft Software Engineering Explore Intern
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lin Hong} \\ \vspace{1pt}
    \small \href{mailto:linlin.hong1@gmail.com}{\underline{linlin.hong1@gmail.com}} $|$
    \href{https://github.com/LinHong149}{\underline{github.com/LinHong149}} $|$
    \href{https://linkedin.com/in/linhongdev}{\underline{linkedin.com/in/linhongdev}} $|$
    \href{https://linhong.dev}{\underline{linhong.dev}} \\
    \vspace{3pt}
    \small 10× Hackathon Winner · Software Engineering Explore Intern · Product-Focused Developer
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Waterloo}{Sept 2025 -- Apr 2029}
      {Bachelor of Computer Science (Co-op)}{}
      \resumeItemListStart
        \resumeItem{President's Scholarship of Distinction, Ted Rogers Future Leaders Scholarship for Women}
        \resumeItem{Relevant coursework: Intro to CS, Data Structures, Algorithm Design, Software Engineering Principles}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Java, C++, JavaScript, TypeScript, Go, Bash, HTML/CSS \\
     \textbf{Technologies:} Git, React, Next.js, Flask, FastAPI, Docker, PostgreSQL, MongoDB, AWS, Azure, GitHub Actions
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote AI}{July 2025 -- Present}
      {Founding Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Shipped \textbf{10+} full-stack features using \textbf{Python}, \textbf{FastAPI}, and React, reducing user onboarding flow time by \textbf{30\%} and increasing weekly active sessions by \textbf{$\sim$25\%}.}
        \resumeItem{Designed and optimized \textbf{backend APIs} and data pipelines on \textbf{PostgreSQL} and \textbf{Redis}, cutting p95 request latency by \textbf{40\%} and eliminating multiple production timeouts.}
        \resumeItem{Improved release reliability by \textbf{introducing CI/CD} with \textbf{GitHub Actions} and code review checklists, driving a noticeable drop in post-release bug reports from teammates.}
      \resumeItemListEnd

    \resumeSubheading
      {FTC Robotics}{Sept 2022 -- June 2025}
      {Senior Software Lead}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Led a \textbf{5-person software team} to design and ship robot features \textbf{end-to-end}, contributing to top-\textbf{5\%} regional rankings and multiple playoff appearances.}
        \resumeItem{Engineered \textbf{telemetry pipelines} in \textbf{C++}/\textbf{Java} to fuse encoder, IMU, and camera data, increasing autonomous path reliability by \textbf{$\sim$20\%} across competition matches.}
        \resumeItem{Implemented and tuned \textbf{PID control} loops that improved autonomous navigation accuracy by \textbf{70\%}, cutting overshoot and oscillation in field tests.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{HomeLab} $|$ \emph{Linux, Docker, Nginx, Cloudflare}}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Deployed and maintained a personal \textbf{Linux server} running \textbf{3+} self-hosted services, achieving \textbf{$>$99\%} uptime over several months with HTTPS via \textbf{Nginx}.}
        \resumeItem{Containerized Node.js apps with \textbf{Docker} and PM2, simplifying updates so new versions ship in minutes instead of hours while keeping downtime near zero.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Spotilike} $|$ \emph{Flask, Next.js, TensorFlow}}{June 2025}
      \resumeItemListStart
        \resumeItem{Built an \textbf{AI-powered} music discovery web app that matches songs to user emotions, integrating \textbf{Flask} backend, \textbf{Next.js} frontend, and \textbf{Spotify API} used by \textbf{50+} test users.}
        \resumeItem{Improved recommendation click-through during user testing by \textbf{$\sim$30\%} after iterating on UI flows and emotion-detection thresholds.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Lofied} $|$ \emph{Python, torchaudio, Docker}}{May 2025}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Python} tool that converts Spotify playlists into lo-fi tracks using \textbf{DSP} and audio processing, processing \textbf{dozens} of tracks per run with a fully automated pipeline.}
        \resumeItem{Won Best Solo Hack \\ Top 6 Overall out of \textbf{200+} hackers at JamHacks 2025, demonstrating end-to-end ownership from idea to working prototype.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Flaim Brain} $|$ \emph{Flask, LangChain, MongoDB}}{Jan 2024}
      \resumeItemListStart
        \resumeItem{Implemented an \textbf{AI study assistant} that supports file uploads, note summarization, and personalized study guides using \textbf{Python}, \textbf{GPT-4}, and \textbf{MongoDB}, cutting manual study-note prep time by \textbf{$\sim$50\%} in user trials.}
        \resumeItem{Placed 4th at Hack the Valley 8 among \textbf{80} teams, validating usability and technical depth through judges' feedback.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
