%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Adapted for Ri Hong
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ri Hong} \\ \vspace{1pt}
    \small \href{mailto:riri.hong@gmail.com}{\underline{riri.hong@gmail.com}} $|$
    \href{https://rihong.ca}{\underline{rihong.ca}} $|$
    \href{https://github.com/Ri-Hong}{\underline{github.com/Ri-Hong}} $|$
    \href{https://linkedin.com/in/ririhong}{\underline{linkedin.com/in/ririhong}}
\end{center}

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Java, C/C++, JavaScript, TypeScript, Go, HTML, CSS \\
     \textbf{Technologies:} React, Next.js, Docker, Kubernetes, Terraform, FastAPI, gRPC, AWS, Linux, PostgreSQL
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Groq}{Sept 2025 -- Dec 2025}
      {Cloud Engineering Intern}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Engineered multi-region infrastructure with Terraform, Kubernetes, and Flux on GCP, enabling horizontally scalable systems and cutting deployment time by 24\% for production workloads.}
        \resumeItem{Designed and launched an observability platform measuring engineering productivity and AI tool adoption, providing actionable insights for 400+ engineers across multiple product teams.}
        \resumeItem{Developed production-ready dashboards and analytics workflows that surfaced correlations between tool usage and code quality, driving data-informed adoption strategies.}
      \resumeItemListEnd

    \resumeSubheading
      {Base Power}{Jan 2025 -- Apr 2025}
      {Markets Infrastructure Engineer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Led fullstack and infrastructure initiatives in a mission-critical trading environment, collaborating with algorithm developers to improve system performance in a Series B (\$850M) startup.}
        \resumeItem{Improved trading simulation reliability and scale by transitioning from local to cloud-native execution using Temporal Cloud, enabling 1000s of auto-retriable workflows and eliminating single-node failure risks.}
        \resumeItem{Discovered and resolved a performance bug in real-time market data transformation logic, reducing complexity from O(n²) to O(n log n) by applying a sort-and-search optimization.}
        \resumeItem{Used OpenTelemetry traces to uncover a performance bottleneck caused by blocking BigQuery writes; implemented non-blocking async publishing using Go routines, achieving a 32\% speedup.}
        \resumeItem{Implemented Protobuf and gRPC to enable seamless communication between Python algorithm services and Go microservices, ensuring type safety and reducing serialization overhead by 20\%.}
        \resumeItem{Rewrote market controller UI using React and Next.js, allowing on-call traders to execute trades within seconds.}
      \resumeItemListEnd

    \resumeSubheading
      {Trend Micro}{Summer 2024}
      {Software Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Upgraded the legacy Deep Security Manager from JDK 8 to JDK 11, modernizing the codebase and enhancing compatibility with contemporary tools for over 250 million global customers.}
        \resumeItem{Revamped the Jenkins CI/CD pipeline to support JDK 11, achieving a 35\% increase in automation efficiency and accelerating deployment timelines by 15\%.}
        \resumeItem{Refactored monolithic codebases into microservices, cutting deployment errors by 30\% and improving scalability for future development.}
        \resumeItem{Troubleshot and resolved over 40 installation and deployment issues on Linux EC2 instances, enhancing system reliability and uptime.}
      \resumeItemListEnd

    \resumeSubheading
      {Walnote.ai}{Aug 2025 -- Present}
      {Founder \& CTO}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Launched an AI platform combining GPT-5 with Manim to auto-generate explainer videos; processed 1,000+ animations with a Celery + FastAPI pipeline.}
        \resumeItem{Accelerated generation by segmenting code generation and running distributed GPU rendering, reducing render latency from 12s to 2s; leveraging a pipelined streaming workflow to deliver near real-time playback.}
        \resumeItem{Scaled secure rendering and delivery with Docker, FFmpeg, Cloudflare R2, and PostgreSQL; raised \$20k pre-seed and led product strategy from prototype to production.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{DistilBERT Sentiment Analysis} $|$ \emph{PyTorch, GCP, Kubernetes, Terraform}}{Sept 2025}
      \resumeItemListStart
        \resumeItem{Engineered a production-grade sentiment analysis service achieving 92.5\% accuracy using DistilBERT, deployed on GKE with Terraform.}
        \resumeItem{Implemented end-to-end MLOps pipeline with MLflow for experiment tracking, DVC for data versioning, and BentoML for model serving.}
        \resumeItem{Optimized training with mixed precision and distributed GPU training with Kubernetes, reducing training time by 40\% while maintaining model accuracy.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Neural Style Transfer Engine} $|$ \emph{PyTorch, CUDA, FastAPI, Docker}}{Sept 2025}
      \resumeItemListStart
        \resumeItem{Engineered a high-performance Neural Style Transfer system with custom CUDA kernels for Gram matrix computation, achieving 8x faster style transfer compared to CPU-only implementation.}
        \resumeItem{Implemented an efficient VGG19-based feature extractor with L-BFGS optimization, delivering production-quality artistic style transfer in under 30 seconds on consumer GPUs.}
        \resumeItem{Built a scalable REST API with FastAPI for style transfer requests, containerized with Docker for easy deployment.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Trasee} $|$ \emph{Pyodide, React, TypeScript, Vite, React Flow}}{Oct 2025}
      \resumeItemListStart
        \resumeItem{Built a real-time Python code visualizer that intelligently recognizes data structures (linked lists, trees, graphs) and renders them interactively in the browser, helping users understand algorithms visually.}
        \resumeItem{Engineered a two-phase static + runtime analysis pipeline using Python's ast module and sys.settrace within Pyodide WebAssembly, enabling accurate inference without external APIs.}
        \resumeItem{Won ``Best Revolutionizing Learning Hack'' at Hack the Valley X among 100+ teams.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{HomeLab} $|$ \emph{Linux, Proxmox, Ansible, Kubernetes}}{Apr 2025}
      \resumeItemListStart
        \resumeItem{Deployed a Kubernetes cluster on Proxmox with Terraform + Ansible, enabling scalable, self-healing microservices and secure HTTPS traffic with Nginx + Cloudflare routing.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{2022 -- 2027}
      {Bachelor of Computer Science (Co-op) · GPA: 3.9/4.0}{}
      \resumeItemListStart
        \resumeItem{Relevant coursework: Algorithms, Data Structures, Object-Oriented Programming, Databases, AI, ML}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

