%-------------------------
% Tailored Resume for NVIDIA Software Engineering Internships (2026)
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lin Hong} \\ \vspace{1pt}
    \small \href{mailto:linlin.hong1@gmail.com}{\underline{linlin.hong1@gmail.com}} $|$
    \href{https://github.com/LinHong149}{\underline{github.com/LinHong149}} $|$
    \href{https://linkedin.com/in/linhongdev}{\underline{linkedin.com/in/linhongdev}} $|$
    \href{https://linhong.dev}{\underline{linhong.dev}} \\
    \vspace{3pt}
    \small 10× Hackathon Winner · Software Engineer · Systems \& Infrastructure Developer
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Sept 2024 -- Apr 2028}
      {Bachelor of Computer Science (Co-op)}{}
      \resumeItemListStart
        \resumeItem{President's Scholarship of Distinction, Ted Rogers Future Leaders Scholarship for Women}
        \resumeItem{Relevant coursework: Algorithm Design, Data Structures, Operating Systems concepts}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Go, Java, C++, JavaScript, TypeScript, Bash, SQL \\
     \textbf{Technologies:} Git, React, FastAPI, Docker, PostgreSQL, Redis, Linux, Nginx, Terraform, PyTorch \\
     \textbf{Systems:} Distributed systems, container orchestration, automation, debugging, performance optimization, microservices
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote AI}{July 2025 -- Present}
      {Founding Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Architected and implemented scalable distributed system using \textbf{FastAPI}, \textbf{Docker} containerization, and \textbf{PostgreSQL} relational database, supporting microservices architecture with \textbf{Redis} pub/sub for real-time event broadcasting.}
        \resumeItem{Optimized large-scale video rendering pipeline by 5× through parallelization with \textbf{Celery} workers, \textbf{Redis} queues, and backend optimizations in \textbf{Python}; implemented scheduling and process control for job orchestration.}
        \resumeItem{Debugged complex system-level issues in production, troubleshooting storage and data platform tools; automated end-to-end infrastructure deployment with \textbf{Git} version control and GitHub Actions CI/CD pipelines.}
        \resumeItem{Designed and deployed cloud storage infrastructure using Cloudflare R2 for object storage, implementing container orchestration and virtualization strategies for scalable service deployment.}
      \resumeItemListEnd

    \resumeSubheading
      {Linovation Design}{Summer 2024}
      {Full Stack Developer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Designed and launched 8 production websites using \textbf{Next.js}, \textbf{React}, \textbf{JavaScript}, and \textbf{TypeScript}, implementing responsive design patterns and OOP principles for maintainable codebases.}
        \resumeItem{Built scalable \textbf{Flask} REST APIs with JWT authentication, \textbf{PostgreSQL} and MongoDB database integrations, and automated deployment workflows using \textbf{Docker} containers and \textbf{Git} version control.}
        \resumeItem{Troubleshot and debugged production issues across frontend and backend systems, optimizing data structures and algorithms for improved performance and user experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{HomeLab} $|$ \emph{Linux, Docker, Nginx, Cloudflare}}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built personal \textbf{Linux} server with SSH key authentication, HTTPS reverse proxying via \textbf{Nginx}, and \textbf{Docker} containerization for secure service deployment.}
        \resumeItem{Configured Cloudflare DNS/routing and implemented health checks with centralized logging for infrastructure automation and monitoring.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Chess Bot} $|$ \emph{PyTorch, Modal, Python}}{June 2025}
      \resumeItemListStart
        \resumeItem{Built AlphaZero-style chess engine with unified policy–value network trained via large-scale self-play reinforcement learning using \textbf{PyTorch}; integrated neural priors into Monte Carlo Tree Search for improved decision-making.}
        \resumeItem{Ran distributed training and self-play generation on \textbf{A100}/\textbf{H100} GPUs via Modal, achieving high-throughput RL cycles with automated checkpoint evaluation and validation frameworks.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Skip the Walk} $|$ \emph{Terraform, Commander.js, Slack API}}{Sept 2024}
      \resumeItemListStart
        \resumeItem{Developed CLI tool automating Domino's ordering and volunteer routing using \textbf{Terraform} for workflow automation and Slack API integration.}
        \resumeItem{Integrated Mappedin indoor navigation with retry logic and logging; won Best Use of Terraform at Hack the North 2024.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

