%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Adapted for Lin Hong
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lin Hong} \\ \vspace{1pt}
    \small \href{mailto:linlin.hong1@gmail.com}{\underline{linlin.hong1@gmail.com}} $|$
    \href{https://github.com/LinHong149}{\underline{github.com/LinHong149}} $|$
    \href{https://linkedin.com/in/linhongdev}{\underline{linkedin.com/in/linhongdev}} $|$
    \href{https://linhong.dev}{\underline{linhong.dev}} \\
    \vspace{3pt}
    \small 10× Hackathon Winner · Analytics Engineering · Data Science
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Waterloo}{Sept 2024 -- Apr 2028}
      {Bachelor of Computer Science (Co-op)}{}
      \resumeItemListStart
        \resumeItem{President's Scholarship of Distinction, Ted Rogers Future Leaders Scholarship for Women}
        \resumeItem{Relevant coursework: Algorithm Design, Data Abstraction, Statistics, Machine Learning, Database Systems}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Java, SQL, JavaScript, TypeScript, C++, Go, Bash \\
     \textbf{Technologies:} PostgreSQL, MongoDB, PyTorch, TensorFlow, Redis, Docker, AWS, Git, FastAPI, Flask
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote AI}{July 2025 -- Present}
      {Founding Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Designed and built real-time data pipelines using \textbf{Python} and Redis pub/sub, processing and broadcasting events into a \textbf{PostgreSQL} database for large-scale analytics.}
        \resumeItem{Optimized large-scale video rendering pipeline, reducing processing time by 5× through segment-based parallelization and distributed processing optimizations.}
        \resumeItem{Collaborated with cross-functional teams to define data models and schemas, enabling efficient querying and real-time analytics dashboards.}
      \resumeItemListEnd

    \resumeSubheading
      {FTC Robotics}{Sept 2022 -- June 2025}
      {Senior Software Lead}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{telemetry pipelines} aggregating encoder, IMU, and camera data from multiple sources into unified robot state estimation with \textbf{signal filtering} and validation logic.}
        \resumeItem{Performed \textbf{data analysis} and \textbf{anomaly detection} on sensor readings, improving reliability by 20\% and doubling response speed through quantified impact analysis.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Chess Bot} $|$ \emph{PyTorch, Modal, \textbf{Python}}}{June 2025}
      \resumeItemListStart
        \resumeItem{Built an AlphaZero-style chess engine with a unified policy–value network trained via large-scale self-play reinforcement learning using \textbf{distributed systems} on A100/H100 GPUs.}
        \resumeItem{Implemented statistical inference and ML models to analyze playing patterns, achieving $\sim$1600 Elo strength through iterative data-driven improvements and automated evaluation.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Spotilike} $|$ \emph{Flask, TensorFlow, \textbf{MongoDB}}}{June 2025}
      \resumeItemListStart
        \resumeItem{Created an AI-driven music discovery platform processing real-time emotion data; designed intuitive \textbf{MongoDB} schemas linking emotion embeddings to music metadata for efficient querying.}
        \resumeItem{Integrated TensorFlow and DeepFace for emotion-aware track recommendations, analyzing user patterns and performing anomaly detection to improve recommendation accuracy.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Flaim Brain} $|$ \emph{Flask, LangChain, \textbf{MongoDB}}}{Jan 2024}
      \resumeItemListStart
        \resumeItem{Implemented an AI mentor platform with \textbf{Flask} backend processing file uploads and note summarization; integrated GPT-4 and \textbf{MongoDB} Atlas Vector Search for semantic data retrieval.}
        \resumeItem{Designed data models and schemas for efficient storage and retrieval of educational content, enabling personalized study guide generation through data-driven insights.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Lofied} $|$ \emph{\textbf{Python}, torchaudio, Docker}}{May 2025}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Python} tool converting Spotify playlists to lo-fi tracks using DSP algorithms and audio processing; implemented data pipelines for batch processing and transformation.}
        \resumeItem{Designed automated processing workflows with \textbf{Docker}-based deployment, enabling scalable data processing and structured output generation for music analysis.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

