%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Adapted for Lin Hong
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lin Hong} \\ \vspace{1pt}
    \small \href{mailto:linlin.hong1@gmail.com}{\underline{linlin.hong1@gmail.com}} $|$
    \href{https://github.com/LinHong149}{\underline{github.com/LinHong149}} $|$
    \href{https://linkedin.com/in/linhongdev}{\underline{linkedin.com/in/linhongdev}} $|$
    \href{https://linhong.dev}{\underline{linhong.dev}} \\
    \vspace{3pt}
    \small 10× Hackathon Winner · Software Engineer · Full-Stack Developer
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Waterloo}{Sept 2024 -- Apr 2028}
      {Bachelor of Computer Science (Co-op)}{}
      \resumeItemListStart
        \resumeItem{President's Scholarship of Distinction, Ted Rogers Future Leaders Scholarship for Women}
        \resumeItem{Relevant coursework: Algorithm Design, Data Abstraction, Software Engineering Principles, Systems Programming}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Java, JavaScript, TypeScript, C++, Go, Bash, HTML/CSS \\
     \textbf{Technologies:} Docker, Git, FastAPI, Flask, PostgreSQL, MongoDB, \textbf{GitHub Actions}, Nginx, Redis, AWS
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walnote AI}{July 2025 -- Present}
      {Founding Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Built scalable REST APIs using \textbf{Python} and \textbf{FastAPI}, \textbf{Dockerized} services with asynchronous workers orchestrated through Redis for high-throughput processing.}
        \resumeItem{Implemented real-time data pipelines with WebSockets and Redis pub/sub, broadcasting events into a \textbf{PostgreSQL} database; deployed with \textbf{GitHub Actions} CI/CD automation.}
        \resumeItem{Optimized large-scale video rendering pipeline, reducing processing time by 5× through segment-based parallelization and backend optimizations.}
      \resumeItemListEnd

    \resumeSubheading
      {FTC Robotics}{Sept 2022 -- June 2025}
      {Senior Software Lead}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Engineered telemetry pipelines aggregating encoder, IMU, and camera data into unified robot state estimation with signal filtering and validation logic.}
        \resumeItem{Designed and implemented PID control algorithms, improving autonomous navigation accuracy by 70\% through systematic testing and iterative refinement.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{HomeLab} $|$ \emph{Linux, Docker, Nginx, Cloudflare}}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built a personal Linux server with SSH key-pair authentication and HTTPS reverse proxying using \textbf{Nginx}; deployed \textbf{Dockerized} Node.js applications with load balancing and CDN integration.}
        \resumeItem{Developed understanding of TCP/IP fundamentals, reverse proxy configurations, and distributed system architectures.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Skip the Walk} $|$ \emph{Terraform, Commander.js, Slack API}}{Sept 2024}
      \resumeItemListStart
        \resumeItem{Built a CLI automation tool using \textbf{JavaScript} to automate Domino's pizza ordering and volunteer routing; integrated \textbf{Terraform} for infrastructure automation and Slack API for notifications.}
        \resumeItem{Won Best Use of Terraform at Hack the North 2024, demonstrating effective automation and workflow optimization.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Spotilike} $|$ \emph{Flask, Next.js, \textbf{JavaScript}, TensorFlow}}{June 2025}
      \resumeItemListStart
        \resumeItem{Created an AI-driven music discovery platform using \textbf{Flask} REST APIs and \textbf{Next.js} frontend with \textbf{JavaScript}, integrating TensorFlow and Spotify API for emotion-aware recommendations.}
        \resumeItem{Designed \textbf{MongoDB} schemas linking emotion embeddings to music metadata, enabling efficient querying and personalized recommendations.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Lofied} $|$ \emph{\textbf{Python}, torchaudio, \textbf{Docker}}}{May 2025}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Python} tool converting Spotify playlists to lo-fi tracks using DSP algorithms; deployed with \textbf{Docker}-based containerization and automated processing pipelines.}
        \resumeItem{Won Best Solo Hack \& Top 6 Overall at JamHacks 2025, demonstrating full-stack development and deployment skills.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

